Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-09-21 paper/paper.Rmd
reesolve [c] from @sbfnk

## Forecast evaluation[c][d] {-}

@@

Our study benefits from having been conducted using forecasts produced in real-time, rather than retrospectively, and submitted to an independent forecast research hub (though we note the overlap between authors on this study and the European forecast hub [@Sherratt2022-ue]).
This means that we can be confident we have captured how our forecast methodology behaves in real-world usage, at least within our study period. 
The downside of this approach is that it was not possible to update the surrogate model over time in response to initial evaluation or to explore other parameterisations that might be more successful of which there are likely several.
However, as our study has been conducted with a focus on reproducibility and openness our findings can be replicated or extended by others regardless of compute availability (due to our use of GitHub actions as a compute platform which is freely available to researchers).
Importantly in this study, we focussed on replicating the forecast hub ensembles' observed behaviour rather than attempting to define an optimal forecast for forecast consumers.
It is possible that if we had instead aimed to develop a forecast methodology that minimised the evaluation criteria we planned to use, especially if we relaxed our assumed compute resource constraints, we would have produced forecasts that performed better relative to the hub ensemble.
However, if we start from the view that the forecast hub ensemble has traits that are desirable for use by policy-makers (i.e robustness and good average performance), which can be found widely in the literature [@Cramer2022-sp; @Bracher2021-wk; @Sherratt2022-ue], then our approach makes sense and may be optimal for producing a "good" forecast.
Our focus on replicating the performance of the hub ensemble is also useful as the surrogate model may highlight some of the emergent behaviour of the ensemble captured in our assumptions, such as auto-correlation across time points, and the growth rate tending towards zero as the forecast horizon increases.
It also highlights some of the differences between our surrogate forecast model and the ensemble that may lead to new insights in understanding the mechanisms leading to the ensembles behaviour, such as the generally poor coverage of the ensemble that could not be explained by the assumptions we used in developing our surrogate methodology.
Whilst we normalised reported cases to be population-adjusted incidence rates our results are conditional on the use of the weighted interval score as an evaluation metric.
As this proper scoring rule measures absolute performance this means that forecasts during periods of higher incidence are given more weight than forecasts from periods of low incidence.
It also means that overprediction is penalised more than underprediction as incidence rates are bounded at zero but relatively weakly bounded by populations at the upper bound (as incidence rates are typically only a small fraction of the overall population).
This bias could explain the relatively poor performance of the surrogate model, compared to the ensemble, despite the surrogate model being comparably well-calibrated.
We considered alternative methods of forecast evaluation that would be robust to this potential source of bias but choose to stick relatively closely to the methodology used by the European forecast hub [@Sherratt2022-ue], aside from the use of population weighting in order to facilitate comparison between forecast locations, as these choices inform the development of submitted models and so are key to our findings.

@@

https://docs.google.com/document/d/1GbAsu1ZZsnm6Wl0WQA0g6LbpRucrLs4gRjpg97DUAA8/edit
[b]Ah, only just saw this - will port my suggestions over.
[c]shouldn't we exclude the surrogate model from the ensemble before comparing performance? Or else mention in the discussion that they aren't completely independent.
[d]I think mention in the discussion as I would like to avoid recomputing.
[e]From SF: Quantify the number of very poorly performing forecasts for the surrogate vs ensemble model.
[f]From SF: what do we consider good / relatively good / poor performance in terms of calibration?
[g]There are quite a few qualitative statements here (see individual comments below) - would be good to quantify with numbers, or otherwise state explicitly in the methods how we evaluate calibration.
[h]Note I've closed out the other related comments in the following section just to be able to see the wood for the trees.

>>>>

## Forecast evaluation[d] {-}

@@

Our study benefits from having been conducted using forecasts produced in real-time, rather than retrospectively, and submitted to an independent forecast research hub (though we note the overlap between authors on this study and the European forecast hub [@Sherratt2022-ue]).
This means that we can be confident we have captured how our forecast methodology behaves in real-world usage, at least within our study period. 
The downside of this approach is that it was not possible to update the surrogate model over time in response to initial evaluation or to explore other parameterisations that might be more successful of which there are likely several.
However, as our study has been conducted with a focus on reproducibility and openness our findings can be replicated or extended by others regardless of compute availability (due to our use of GitHub actions as a compute platform which is freely available to researchers).
An additional downside to this approach is that the hub ensemble includes forecasts from our surrogate model, increasing the similarity between the two approaches.
This is difficult to avoid without retrospectively re-calculating the ensemble using the same approach as taken by the hub which would reduce the independence of the hub ensemble as a source of truth to compare our forecasts against.
Given the number of forecasts submitted in most locations, and the Europeans forecast hubs practice of not calculating an ensemble when fewer than 3 independent forecasts were available, the bias on our results caused by this limitation should be relatively small.
Importantly in this study, we focussed on replicating the forecast hub ensembles' observed behaviour rather than attempting to define an optimal forecast for forecast consumers.
It is possible that if we had instead aimed to develop a forecast methodology that minimised the evaluation criteria we planned to use, especially if we relaxed our assumed compute resource constraints, we would have produced forecasts that performed better relative to the hub ensemble.
However, if we start from the view that the forecast hub ensemble has traits that are desirable for use by policy-makers (i.e robustness and good average performance), which can be found widely in the literature [@Cramer2022-sp; @Bracher2021-wk; @Sherratt2022-ue], then our approach makes sense and may be optimal for producing a "good" forecast.
Our focus on replicating the performance of the hub ensemble is also useful as the surrogate model may highlight some of the emergent behaviour of the ensemble captured in our assumptions, such as auto-correlation across time points, and the growth rate tending towards zero as the forecast horizon increases.
It also highlights some of the differences between our surrogate forecast model and the ensemble that may lead to new insights in understanding the mechanisms leading to the ensembles behaviour, such as the generally poor coverage of the ensemble that could not be explained by the assumptions we used in developing our surrogate methodology.
Whilst we normalised reported cases to be population-adjusted incidence rates our results are conditional on the use of the weighted interval score as an evaluation metric.
As this proper scoring rule measures absolute performance this means that forecasts during periods of higher incidence are given more weight than forecasts from periods of low incidence.
It also means that overprediction is penalised more than underprediction as incidence rates are bounded at zero but relatively weakly bounded by populations at the upper bound (as incidence rates are typically only a small fraction of the overall population).
This bias could explain the relatively poor performance of the surrogate model, compared to the ensemble, despite the surrogate model being comparably well-calibrated.
We considered alternative methods of forecast evaluation that would be robust to this potential source of bias but choose to stick relatively closely to the methodology used by the European forecast hub [@Sherratt2022-ue], aside from the use of population weighting in order to facilitate comparison between forecast locations, as these choices inform the development of submitted models and so are key to our findings.

@@

https://docs.google.com/document/d/1GbAsu1ZZsnm6Wl0WQA0g6LbpRucrLs4gRjpg97DUAA8/edit
[b]Ah, only just saw this - will port my suggestions over.
[d]I think mention in the discussion as I would like to avoid recomputing.
[e]From SF: Quantify the number of very poorly performing forecasts for the surrogate vs ensemble model.
[f]From SF: what do we consider good / relatively good / poor performance in terms of calibration?
[g]There are quite a few qualitative statements here (see individual comments below) - would be good to quantify with numbers, or otherwise state explicitly in the methods how we evaluate calibration.
[h]Note I've closed out the other related comments in the following section just to be able to see the wood for the trees.
